---
title: "align_files_internal"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{align_files_internal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(soundlocalization)
library(ggplot2)
library(lubridate)
library(tidyverse)
```

# this file contains the steps necessary for align files. 




Lets do by example. 
Here is a list of recordings taken on a line array of approx 4 m between receptors. 


```{r}
files<-list(
 system.file("extdata", "Grabacion_2_andrea.wav", package = "soundlocalization"),
 system.file("extdata", "Grabacion_1_joaco.wav", package = "soundlocalization"),
 system.file("extdata", "Grabacion_1_cande.wav", package = "soundlocalization"),
 system.file("extdata", "Grabacion_3_luciano.wav", package = "soundlocalization")
 )
labels=c("Andrea","Joaco","Candela","Luciano")
geo_locations=rbind(geo_coordinates(lat=-34.61410605441556,
                                lon= -58.38404404725583),
                geo_coordinates(-34.614103295104634, -58.3839950969408),
                geo_coordinates(-34.6140999839314, -58.383942123312224),
                geo_coordinates(-34.61409722462029, -58.38389920796756))

time_of_recording=ymd_hm("2022-09-03 10:52",tz="America/Buenos_Aires")
```


We use the function loadwavfiles to read all the recordings at once.

```{r}
recordings<-recordings(files = files,
                       labels = labels,
                       geo_locations = geo_locations, 
                       time_of_recording = time_of_recording)

```


Lets see the organization of recordings
```{r}
str(recordings)
```
We see that it is comprised by a list of two subojects: 
1. meta_data, a data.frame with information on 
 + the directory, 
 + filename, 
 + number of samples, 
 a boolean indicating if the recording was stereo, 
 the frequency of sampling, 
 the number of bits and 
 if the pcm is complied. 

2. signal: a list of integer vectors of different sizes
  The signal contains the actual recording, in a limited number of bits (16)


Now, let see a graphical representation of the sound recorded at each site. 

```{r}
sound_plot(recordings)

```



Now, if we want to do a fourier transform, we better use the same number of samples. So we need to homogenize their size. 
We build a function exactly for that purpose. 

```{r}
i_same_length=indexes_for_same_length(recordings)
str(i_same_length)
```

we see that the output of this function is a list of two integer vectors: i_start and i_end. We see that the i_end[1] is equal to the size of the first signal, the idea is that by applying those indexes we obtain recordings of the same length. 

For this purpose we use another helper function
```{r}
apply_frame(recordings,i_same_length)->e_recordings
str(e_recordings)
```
we see that the output contains the indexes for start and end and a long matrix with the truncated signal 


Now, we need to AZapply a hanning window to avoid artifacts from the fft. 
```{r}
h_recordings=apply_hanning_window(e_recordings)
str(h_recordings)
```

Lets see the aspect of the truncated recordings
```{r}
sound_plot(h_recordings)
```



Now we are ready to calculate the fourier transforms

```{r}
f_signal=calculate_ffts(h_recordings)
str(f_signal)
```




now we can calculate the crosscorrelations between the recordings, so we can come up close to be able to align them
```{r}
ccf_signal=calculate_list_of_cross_correlations(h_recordings)
str(ccf_signal)  
```
```{r}
gcc_signal=calculate_list_of_gcc_phase(e_recordings, remove_if_z_is_greater_than = 5)
str(gcc_signal)  


```
Lets plot the gcc-phase 

```{r}
gcc_phase_data(e_recordings,
              t_start = 0,
              t_end = 100,
           min_freq=0,
           max_freq=10000,
           remove_if_z_is_greater_than=5,

           freq_filter = F)->gcc_data

```

```{r}
str(gcc_data)
```


```{r}

data_for_plot_gcc_phase(gcc_data,lag_window_in_meters = 8000, max_points =1000)->gcc_data_for_plot
str(gcc_data_for_plot)

```
```{r}
gcc_phase_plot(gcc_data_for_plot)
```


```{r}
rrange<-function(v) diff(range(v))
data_for_plot_gcc_phase(gcc_data,lag_window_in_meters = 100, decimating_operation = "rrange",max_points = 10000)->gcc_data_for_plot_mean
gcc_phase_plot(gcc_data_for_plot_mean)

```

```{r}
gcc_phase_data_for_tri_plot(gcc_data,lag_window_in_meters=8000,        max_points=100,keep_the_best_n =200,keep_if_z_is_greater_than = 100)->tri_d100
```


```{r}
#str(tri_d)
gcc_phase_tri_plot(tri_d100)
```

```{r}
gphase_filter_peaks(gcc = h_recordings,t_start = 0,t_end = 100,lag_window_in_meters = 800,max_points = 100,keep_the_best_n = 100)->peaks
```


```{r}
gcc_phase_plot(tri_d100,lag_window_in_meters = 800)

```



now, lets find out the lags

```{r}
max_ccf=max_lag_ccf(ccf_signal)
str(max_ccf)
```
```{r}
calc_lag_ccf(max_ccf )->maxs_ccf
str(maxs_ccf)
```



now we can optimize the lags to find the better combination
```{r}
optimize_delays_from_ccf(ccf_signal,max_ccf,maxs_ccf)->opt_ccf
str(opt_ccf)
```


