---
title: "soundlocalization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{soundlocalization}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(soundlocalization)
library(ggplot2)
library(lubridate)
```

The purpose of this package is to provide tools for isolating and
localizing the source of sounds from an array of receptors, not
necessary arranged in a regular order.

Lets do by example. Here is a list of recordings taken on a line array
of approx 4 m between receptors.

```{r}
files <- list(
  system.file("extdata", "Grabacion_2_andrea.wav", package = "soundlocalization"),
  system.file("extdata", "Grabacion_1_joaco.wav", package = "soundlocalization"),
  system.file("extdata", "Grabacion_1_cande.wav", package = "soundlocalization"),
  system.file("extdata", "Grabacion_3_luciano.wav", package = "soundlocalization")
)
labels = c("Andrea", "Joaco", "Candela", "Luciano")
geo_locations = rbind(
  geo_coordinates(
    lat = -34.61410605441556,
    lon = -58.38404404725583
  ),
  geo_coordinates(
    lat = -34.614103295104634,
    lon = -58.3839950969408
  ),
  geo_coordinates(
    lat = -34.6140999839314,
    lon = -58.383942123312224
  ),
  
  geo_coordinates(
    lat = -34.61409722462029,
    lon = -58.38389920796756
  )
)
time_of_recording = ymd_hm("2022-09-03 10:52", tz = "America/Buenos_Aires")
```

The receptors were placed in the same line (all the xs were equal) at
distances of 5, 4 and 4 meters.

We use the function recordings to read all the recordings at once.

```{r}
rec<-recordings(files = files,
                       labels = labels,
                       geo_locations = geo_locations, 
                       time_of_recording = time_of_recording)

```

Lets see the organization of rec

```{r}
str(rec)
```

We see that it is a dataframe with information on + a label for each
recording, + precise ubication in time (day and time of recording) and
space (latitude and longitude in a meter precision) + the directory and
filename of the recording, + information on the recording such as number
of samples, a boolean indicating if the recording was stereo, the
frequency of sampling, the number of bits and if the pcm is complied. +
signal: a list of integer vectors of different sizes for each one of the
recordings. The signal contains the actual recording, in a limited
number of bits (16)

Now, let see a graphical representation of the sound recorded at each
site.

```{r}
sound_plot(recordings = rec )

```

the recordings were not sinchronized but we can use the cross
correlation function to approximately sinchronize them

```{r}
a_recordings<-align_recordings(rec)
str(a_recordings)
```

Now, lets analyze the spectral components of the recordings in 10
seconds frames

```{r}
for (i in 1:length(a_recordings$framed_raw_signal))
{
  spectro_plot(recordings = a_recordings,i,start = 118,end=120.8,min_freq = 00,max_freq = 10000,listen = T)

}
```

```{r}
spectro_plot_luc(rec = a_recordings,start = 118,end=120.8,min_freq = 00,max_freq = 6000,window_length_meters = 20)

```

Lets see the cross correlation plot

```{r}
  gcc_phase_plot(rec = a_recordings,t_start =  118,t_end = 120.8,min_freq = 500,max_freq = 6000,lag_window_in_meters = 30,remove_if_z_is_greater_than=5)
```
```{r}
plot_shared_peaks(gcc =  a_recordings,t_start =  118,t_end = 120.8,min_freq = 500,max_freq =  6000,lag_window_in_meters = 30, show_greatest_n_peaks = 5)

```

```{r}
luciano_voice<-set_source_list(names=c("luciano_voice"),x_pos_min = -2,x_pos_max = 2, y_pos_min = 11.3,y_pos_max = 15.3,min_freq =500,max_freq = 2000 )

luciano_bird<-set_source_list(names=c("luciano_bird"),x_pos_min = 1,x_pos_max = 50, y_pos_min = -10,y_pos_max = 25,min_freq =3000,max_freq = 6000 )

luciano_street_noise<-set_source_list(names=c("luciano_street_noise"),x_pos_min = 20,x_pos_max = 200, y_pos_min = -200,y_pos_max = 200,min_freq =000,max_freq = 500 )
```

```{r}
luciano_frame<-set_frame_list(t_start = 118,t_end=120.8,sourceList = c(luciano_voice$names,luciano_bird$names,luciano_street_noise$names))
str(luciano_frame)
```

```{r}
luciano_frame_sources<-rbind(luciano_voice,luciano_bird,luciano_street_noise)
luciano_frame_sources
```

```{r}
for (i in 1:length(a_recordings$framed_raw_signal))
{
  spectro_plot(recordings = a_recordings,i,start = 120.8,end=122,listen=T,min_freq = 00,max_f=5000,listen_freq = 1)
  
 # listen(recordings = a_recordings,i,start = 120.8,end=125)
}
```


```{r}
andrea_voice<-set_source_list(names=c("andrea_voice"),x_pos_min = -2,x_pos_max = 2, y_pos_min = -2,y_pos_max = 2,min_freq =500,max_freq = 3500 )
joaquin_voice<-set_source_list(names=c("joaquin_voice"),x_pos_min = -2,x_pos_max = 2, y_pos_min = 2.5,y_pos_max = 6.5,min_freq =500,max_freq = 2500 )

andrea_bird<-set_source_list(names=c("andrea_bird"),x_pos_min = 1,x_pos_max = 50, y_pos_min = -10,y_pos_max = 25,min_freq =3000,max_freq = 6000 )

andrea_street_noise<-set_source_list(names=c("andrea_street_noise"),x_pos_min = 20,x_pos_max = 200, y_pos_min = -200,y_pos_max = 200,min_freq =000,max_freq = 500 )
```

```{r}
andrea_frame<-set_frame_list(t_start = 120.8,t_end=122,sourceList = c(andrea_voice$names,joaquin_voice$names,andrea_bird$names#,andrea_street_noise$names)
                                                                      ))

andrea_frame_sources<-rbind(andrea_voice,joaquin_voice,andrea_bird#,andrea_street_noise
                            )
```

```{r}
  spectro_plot(recordings = a_recordings,4,start = 0,end=10,listen=F,min_freq = 2500,max_f=4500,listen_freq = 1)

```

```{r}
  spectro_plot_luc(rec =  a_recordings,i,start = 122,end=127, min_freq = 500,max_freq = 4000)
 # listen(recordings = a_recordings,i,start = 120.8,end=125)

candela_voice<-set_source_list(names=c("candela_voice"),x_pos_min = -2,x_pos_max = 2, y_pos_min = 7,y_pos_max = 11,min_freq =500,max_freq = 3000 )

candela_bird<-set_source_list(names=c("candela_bird"),x_pos_min = 1,x_pos_max = 50, y_pos_min = -10,y_pos_max = 25,min_freq =3000,max_freq = 6000 )


candela_street_noise<-set_source_list(names=c("candela_street_noise"),x_pos_min = 20,x_pos_max = 200, y_pos_min = -200,y_pos_max = 200,min_freq =000,max_freq = 500 )
```

```{r}
candela_frame<-set_frame_list(t_start = 122,t_end=127,sourceList = c(candela_voice$names,candela_bird$names,candela_street_noise$names))
candela_frame_sources<-rbind(candela_voice,candela_bird,candela_street_noise)
```

```{r}
for (i in 1:length(a_recordings$framed_raw_signal))
{
  spectro_plot(recordings = a_recordings,i,start = 0,end=9,listen=T, min_freq = 2500,max_freq = 4000)
 # listen(recordings = a_recordings,i,start = 120.8,end=125)
}

initial_bird_1<-set_source_list(names=c("initial_bird_1"),x_pos_min = 1,x_pos_max = 50, y_pos_min = -20,y_pos_max = 25,min_freq =2000,max_freq = 6000 )

initial_bird_2<-set_source_list(names=c("initial_bird_2"),x_pos_min = 1,x_pos_max = 50, y_pos_min = -10,y_pos_max = 25,min_freq =2000,max_freq = 6000 )

initial_bird_3<-set_source_list(names=c("initial_bird_3"),x_pos_min = 1,x_pos_max = 50, y_pos_min = -10,y_pos_max = 35,min_freq =2000,max_freq = 6000 )
initial_street_noise<-set_source_list(names=c("initial_street_noise"),x_pos_min = 20,x_pos_max = 200, y_pos_min = -200,y_pos_max = 200,min_freq =000,max_freq = 500 )
```

```{r}
initial_frame<-set_frame_list(t_start = 0,t_end=9,sourceList = c(initial_bird_1$names,initial_bird_2$names,initial_bird_3$names#,initial_street_noise$names
                                                                 ))
initial_frame_sources<-rbind(initial_bird_1,initial_bird_2,initial_bird_3#,initial_street_noise
                             )

```

```{r}
all_frames=rbind(luciano_frame,andrea_frame,candela_frame,initial_frame)

```

```{r}
all_frames<-frame_to_signal_fft(a_recordings,all_frames = all_frames)
str(all_frames)
all_luciano_frames<-frame_to_signal_fft(a_recordings,all_frames = luciano_frame)
```

```{r}
all_initial_frames<-frame_to_signal_fft(a_recordings,all_frames = initial_frame)

str(all_initial_frames)
```

```{r}
luciano_ccf_frame<-calculate_list_of_cross_correlations(all_luciano_frames)
```

```{r}

all_receptors$x=all_receptors$x_min/2+all_receptors$x_max/2
all_receptors$y=all_receptors$y_min/2+all_receptors$y_max/2

locatiogram(single_frames = luciano_ccf_frame,receptors = all_receptors)->locatio_luciano
```

```{r}
juicy_frames<-select_juicy_freq(all_frames = all_frames,fs = recordings$meta_data$fs[1],min_freq = 1000,fraction = 0.002)

luciano_juicy_frames<-select_juicy_freq(all_frames = all_luciano_frames,fs = recordings$meta_data$fs[1],min_freq = 500,fraction = 0.05)

str(luciano_juicy_frames)
```

```{r}
initial_juicy_frames<-select_juicy_freq(all_frames = all_initial_frames,fs = recordings$meta_data$fs[1],min_freq = 4000,fraction = 0.002)

str(initial_juicy_frames)
```

```{r}
all_sources=rbind(luciano_frame_sources,andrea_frame_sources,candela_frame_sources,initial_frame_sources)
all_sources


```

get the receptors

```{r}


all_receptors<-get_receptorList(labels=labels,geo_locations = geo_locations,origin =geo_locations[1,],x_axis = geo_locations[2,],pos_error = 2,Gain_error_factor =200,lag_error = 30,all_frames
  )
all_receptors
```

```{r}
luciano_receptors<-get_receptorList(labels=labels,geo_locations = geo_locations,origin =geo_locations[1,],x_axis = geo_locations[2,],pos_error = 2,Gain_error_factor =200,lag_error = 30,all_luciano_frames
  )
luciano_receptors

```

Lets localize and isolate the proposed sources

```{r}
optimize_localizations(rec,all_frames=juicy_frames,all_receptors = all_receptors,all_sources =all_sources ,lambda = 0,algorithm = "stogo",maxeval = 1000)
```

```{r}
optimize_localizations(rec,all_frames=luciano_juicy_frames,all_receptors = luciano_receptors,all_sources =luciano_frame_sources ,lambda = 0)->luciano_opt

```

```{r}
optimize_localizations(rec,all_frames=initial_juicy_frames,all_receptors = all_receptors,all_sources =initial_frame_sources ,lambda = 0,algorithm = "sbplx")->initial_opt

```
