---
title: "understanding_gcc_phase"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{understanding_gcc_phase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(soundlocalization)
library(tidyverse)
```

```{r}
fs=44100
trace_duration=1
nsamples=fs*trace_duration
y0=simulate_harmonic_signal(fs=44100,trace_duration = trace_duration, fundamental_freq = 1000, harmonic_amplitudes = c(1,0.2,0.8,0.02,0.7,0.1,0.4,0.1),tstart = 0.1,t_end=0.4)
y01=simulate_harmonic_signal(fs=44100,trace_duration = trace_duration, fundamental_freq = pi*1000, harmonic_amplitudes = c(1,0.2,0.8,0.02,0.7,0.1,0.4,0.1),tstart = 0.3,t_end=0.3+pi*0.01)


y1=simulate_harmonic_signal(fs=44100,trace_duration = 1, fundamental_freq = 1000, harmonic_amplitudes = c(1,0.2,0.8,0.02,0.7,0.1,0.4,0.1),tstart = 0.1+0.01,t_end=0.4+0.01)
lags=-(nsamples/2):(nsamples/2-1)/fs

y11=simulate_harmonic_signal(fs=44100,trace_duration = 1, fundamental_freq = pi*1000, harmonic_amplitudes = c(1,0.2,0.8,0.02,0.7,0.1,0.4,0.1),tstart = 0.3+0.02,t_end=0.3+pi*0.01+0.02)
lags=-(nsamples/2):(nsamples/2-1)/fs

gcc_phase<-function(y0,y1,hanning=T)
{
  nsamples=length(y0)
  hn=1
  if (hanning)
   hn = seewave::ftwindow(nsamples,wn="hanning")
  Y0=fft(y0*hn)
Y1=fft(y1*hn)
i_lags=c((nsamples/2):nsamples,1:(nsamples/2-1))
gcc=Re(fft((Conj(Y0)*Y1)/Mod((Conj(Y0)*Y1)),inverse = T))[i_lags]
}

dgcc_phase<-function(y0,y1,hanning=T)
{
  nsamples=length(y0)
  w=c(0:(nsamples/2-1),(-nsamples/2):-1)*fs/nsamples
  hn=1
  if (hanning)
   hn = seewave::ftwindow(nsamples,wn="hanning")
  Y0=fft(y0*hn)
Y1=fft(y1*hn)
i_lags=c((nsamples/2):nsamples,1:(nsamples/2-1))
dgcc=Re(fft((Conj(Y0)*Y1)/Mod((Conj(Y0)*Y1))*1i*w,inverse = T))[i_lags]
}

Igcc_phase<-function(y0,y1,hanning=T)
{
  nsamples=length(y0)
  w=c(0:(nsamples/2-1),(-nsamples/2):-1)*fs/nsamples
  hn=1
  if (hanning)
   hn = seewave::ftwindow(nsamples,wn="hanning")
  Y0=fft(y0*hn)
Y1=fft(y1*hn)
i_lags=c((nsamples/2):nsamples,1:(nsamples/2-1))
dgcc=Re(fft((Conj(Y0)*Y1)/Mod((Conj(Y0)*Y1))/1i/w,inverse = T))[i_lags]
}


```




```{r}

f0= 1000*3
f1= 1000*1.5

dt0=0.01
dt1=0.016

ncyclesdur0=30
ncyclesdur1=20

tstart0=0.45
tstart1=0.55

dur0=ncyclesdur0/f0
dur1=ncyclesdur1/f1

A0=c(1,0.2,0.8,0.14,0.5)
A1=c(1,0.3,0.7,0.31,0.57)

t=1:nsamples*fs

y0=simulate_harmonic_signal(fs=44100,trace_duration = trace_duration, fundamental_freq = f0, harmonic_amplitudes = A0,tstart = tstart0,t_end=tstart0+dur0)
y01=simulate_harmonic_signal(fs=44100,trace_duration = trace_duration, fundamental_freq = f1, harmonic_amplitudes = A1,tstart = tstart1,t_end=tstart1+dur1)


y1=simulate_harmonic_signal(fs=44100,trace_duration = 1, fundamental_freq = f0, harmonic_amplitudes = A0,tstart = tstart0+dt0,t_end=tstart0+dur0+dt0)
lags=-(nsamples/2):(nsamples/2-1)/fs

y11=simulate_harmonic_signal(fs=44100,trace_duration = 1, fundamental_freq = f1, harmonic_amplitudes = A1,tstart = tstart1+dt1,t_end=tstart1+dur1+dt1)
lags=-(nsamples/2):(nsamples/2-1)/fs
gcc=gcc_phase(y0+rnorm(nsamples)*0.001+y01,y1+rnorm(nsamples)*0.0001+y11,hanning = T)
dgcc=Igcc_phase(y0+rnorm(nsamples)*0.001+y01,y1+rnorm(nsamples)*0.0001+y11,hanning = T)

ggplot()+geom_line(aes(x=lags,y = gcc))+scale_x_continuous(limits=c(min(dt0,dt1)-0.1*abs(dt0-dt1), max(dt0,dt1)+0.1*abs(dt0-dt1)))

ggplot()+geom_line(aes(x=lags,y = gcc))+scale_x_continuous(limits=c(min(dt0,dt1)-5*abs(dt0-dt1), max(dt0,dt1)+5*abs(dt0-dt1)))

ggplot()+geom_line(aes(x=lags,y = gcc))

ggplot()+geom_line(aes(x=lags,y = dgcc))+scale_x_continuous(limits=c(min(dt0,dt1)-0.1*abs(dt0-dt1), max(dt0,dt1)+0.1*abs(dt0-dt1)))

ggplot()+geom_line(aes(x=lags,y = dgcc))+scale_x_continuous(limits=c(min(dt0,dt1)-5*abs(dt0-dt1), max(dt0,dt1)+5*abs(dt0-dt1)))

ggplot()+geom_line(aes(x=lags,y = dgcc))

ggplot()+geom_line(aes(x=t,y = y0))
ggplot()+geom_line(aes(x=t,y = y01))
ggplot()+geom_point(aes(x=1:(nsamples/2)/nsamples*fs,y=abs(fft(y0))[1:(nsamples/2)]))
ggplot()+geom_point(aes(x=1:(nsamples/2)/nsamples*fs,y=abs(fft(y01))[1:(nsamples/2)]))


```

f0= 1000*3
f1= 1000*1.5

dt0=0.01
dt1=0.015

ncyclesdur0=30
ncyclesdur1=20

tstart0=0.45
tstart1=0.55

dur0=ncyclesdur0/f0
dur1=ncyclesdur1/f1

A0=c(1,0.2,0.8,0.14,0.5)
A1=c(1,0.3,0.7,0.31,0.57)


y0=simulate_harmonic_signal(fs=44100,trace_duration = trace_duration, fundamental_freq = f0, harmonic_amplitudes = A0,tstart = tstart0,t_end=tstart0+dur0)
y01=simulate_harmonic_signal(fs=44100,trace_duration = trace_duration, fundamental_freq = f1, harmonic_amplitudes = A1,tstart = tstart1,t_end=tstart1+dur1)


y1=simulate_harmonic_signal(fs=44100,trace_duration = 1, fundamental_freq = f0, harmonic_amplitudes = A0,tstart = tstart0+dt0,t_end=tstart0+dur0+dt0)
lags=-(nsamples/2):(nsamples/2-1)/fs

y11=simulate_harmonic_signal(fs=44100,trace_duration = 1, fundamental_freq = f1, harmonic_amplitudes = A1,tstart = tstart1+dt1,t_end=tstart1+dur1+dt1)
lags=-(nsamples/2):(nsamples/2-1)/fs
gcc=gcc_phase(y0+rnorm(nsamples)*0.001+y01,y1+rnorm(nsamples)*0.0001+y11,hanning = F)
ggplot()+geom_line(aes(x=lags,y = gcc))+scale_x_continuous(limits=c(min(dt0,dt1)-0.1*abs(dt0-dt1), max(dt0,dt1)+0.1*abs(dt0-dt1)))
ggplot()+geom_line(aes(x=lags,y = gcc))+scale_x_continuous(limits=c(min(dt0,dt1)-5*abs(dt0-dt1), max(dt0,dt1)+5*abs(dt0-dt1)))
#ggplot()+geom_line(aes(x=lags,y = gcc))+scale_x_continuous(limits=c(0,0.03))
ggplot()+geom_line(aes(x=lags,y = gcc))
ggplot()+geom_line(aes(x=t,y = y0))
ggplot()+geom_line(aes(x=t,y = y01))
ggplot()+geom_point(aes(x=1:(nsamples/2)/nsamples*fs,y=abs(fft(y0))[1:(nsamples/2)]))
ggplot()+geom_point(aes(x=1:(nsamples/2)/nsamples*fs,y=abs(fft(y01))[1:(nsamples/2)]))


```

